Digital History in Finland, 1488-1828

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
author plots

>>>>

```{r 20151209-HDH-topplace, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=5}
top_plot(dfo, "publication_place", 10) + ylab("Title count (n)") + ggtitle("Top publication places")
```

```{r 20151209-HDH-toptopic, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
top_plot(dfo, "subject_topic", 10) + ylab("Title count (n)") + ggtitle("Top themes")
```

```{r 20151209-HDH-topg, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=9}
topg <- setdiff(names(rev(sort(table(dfo$gatherings))))[1:6], "NA")
dfs <- dfo %>%
    filter(gatherings %in% topg & publication_year > 1650) %>%
    group_by(publication_decade, gatherings) %>% tally()
dfs$gatherings <- order_gatherings(dfs$gatherings)    
p <- ggplot(dfs, aes(x = publication_decade, y = n, color = gatherings)) + geom_point(size = 3) + geom_smooth(fill = "lightgray", size = 2, alpha = 0.2) + ggtitle("Top gatherings timeline") + ylim(c(0, max(dfs$n)))
print(p)
```
